Incentivizing Exploration by Heterogeneous Users

### 2018-02-06 algorithm.tex
almost finished regret proof

\dkcomment{Keeping this around for now.}
Notation: $t_s$ is end time for phase $s$.

@@

Let $\tau$ be any stopping time that is almost surely \dkcomment{What
  exactly do we mean by this here?} in phase $s$,
with respect to the filtration
$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
                          \PayA{1}, \ldots, \PayA{t},
                          \ObsV{1}, \ldots, \ObsV{t})$.
Then, for all $s \geq \LatePhase$,
with probability (over the past history) at least 
$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
\dkcomment{We should clarify what the probability is over. It seems to
  be over the past history, but not the current agent.}
all agent types $\AgV = \AgentV{\tau}$ with
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$
will pull their best arm, i.e.,
$\argmax \SET{\AgV \cdot \ArmEV{\tau}{i}} = \Best{\AgV}$
\end{corollary}

@@

Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
$\tau$ such that
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) > 2\Diam d x$.
Let $i \neq \Best{\AgV}$ be any other arm;
its true reward is much smaller than from the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
\ArmEV{\tau}{i} is estimated accurately to within $x$, 
we get that 
$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d x$
and
$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
& =
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
& > -\Diam d x + 2 \Diam d x - \Diam d x
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will in fact choose
the optimal arm in the high-probability event.
\end{proof}

@@

As we can see later in our proof, we only need $\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be finite. Intuitively, assumption~\ref{A1} states that there are not many agents who are indifferent between their best arm and the second best arm.

@@

We distinguish two types of agents, based on whether their preference
for their best arm over the second-best arm is ``large'' or ``small''.
To be more precise, we will define (with hindsight) a time-dependent
cutoff $g(t)$, and for any agent type $\AgV \in \FirstTwo{i}{i'}$,
distinguish whether $\AgV \cdot (\ArmV{i} - \ArmV{i'}) \geq g(t)$ or not.

By Lemma~\ref{lem:sdelta}, the total measure of agents whose
preference is ``small'' in this sense is at most
$\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$ for all $t$.
\dkcomment{Put here whatever upper bound we use for these agents.}

\dkcomment{I edited up to this point. Some notation has been replaced
  below with query-replace, but not all of it.}

For the regret incurred when we let the agents play myopically at time $t$ in the $s\geq s_0$ phase, it consists of the following two components:
\begin{itemize}
\item For those user who will pull an arm that occurs regret greater than $g(t)$: if all arms estimation errors are within $\frac{g(t)}{2\Diam d}$, then based on the same argument as \eqref{equ:choice}, this will never happen. We define a sequence of stopping time $\tau_{s}^{k}$ to be the \Kth{k}
time period in the \Kth{s} phase.
For $k > t_{s}-t_{s-1}$, we define $\tau_{s}^{k}=\infty$.
For $\tau_{s}^{k}=t$, the probability of users occur regret greater than $g(t)$ is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$,
and the expected regret is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR$.
We denote the regret incurred by these agents by $r_1(\tau_{s}^{k})$.
For $k > t_{s}-t_{s-1}$, we define $r_1(\tau_{s}^{k})=0$.

\item For those user who will pull an arm that occurs regret smaller than $g(t)$: if the user pulls his/her best arm, no regret occurs. Otherwise, we know his/her utility difference between best and second best arm is smaller than $g(t)$. Further, we know this happens with probability \AlmostTied{g(t)} at each time,
and the regret is bounded above by
$\AlmostTied{g(t)} \cdot g(t) \leq \TieDensity \cdot (g(t))^2$.
We denote the regret incurred by these agents as $r_2(t)$.
\end{itemize}

Thus, the cumulative expected regret incurred up to time $T$ when we
let the agent play myopically is bounded above by:
\begin{align}
\Expect{\sum_{t=1}^{T}\Regret{t}} 
& = \Expect{\sum_{t=1}^{t_{\LatePhase}} \Regret{t} + \sum_{t=t_{\LatePhase}}^{T}(r_1(t)+r_2(t))}  \nonumber \\
& \leq \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T}\sum_{t=t_{s}}^{t_{s+1}-1}r_1(t)}
     + \Expect{\sum_{t=1}^{T}r_2(t)} \nonumber \\
& = \sum_{s=1}^{\LatePhase} \ARMNUM \MAXR s
     + \Expect{\sum_{s=\LatePhase}^{T} \sum_{k=1}^{\infty}r_1(\tau_{s}^{k})}
     + \Expect{\sum_{t=1}^{T}r_2(t)}. \label{chap5:equ:r1}
\end{align}
Since
\begin{align}
& E\left[\sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}r_1(\tau_{n}^{k})\right] \nonumber\\
= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})] \nonumber \\
= &  \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}(E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty)+E[r_1(\tau_{s}^{k})|\tau_{s}^{k}=\infty]\times P(\tau_{s}^{k}=\infty)) \nonumber \\
= & \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty), \nonumber
\end{align}

we have
\begin{align}
\eqref{chap5:equ:r1}= & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\sum_{k=1}^{\infty}E[r_1(\tau_{s}^{k})|\tau_{s}^{k}<\infty]\times P(\tau_{s}^{k}<\infty) + E\left[\sum_{t=1}^{T}r_2(t)\right] \nonumber \\
\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=\LatePhase}^{T}\left[\sum_{k=1}^{\infty}24\ARMNUM d\exp\left(-\frac{1.8s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right) R\times P(\tau_{s}^{k}<\infty) \right]+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\
\leq & \sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24 \ARMNUM  d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2. \label{chap5:equ:regret}
\end{align}

Thus the cumulative regret at time $T$ is bounded above by
\begin{align}
&\sum_{s=1}^{\LatePhase}\ARMNUM \MAXR s + \sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2  +\nonumber \\
&O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right). \nonumber 
\end{align}

For a fixed $T$, we only need to minimize the following two terms since all others are constant:

\begin{align}
\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity \cdot (g(t))^2. \label{equ:regret}
\end{align}

If we set $g^2(t)=\frac{2\log(T)\times 64\Diam^2 d^2\sigma^2}{1.8t}$, then
\begin{align}
&\sum_{s=1}^{T} 24\ARMNUM d\exp\left(-\frac{1.8s f(s)^2}{64 \Diam^2 d^2\sigma^2}\right)\times \MAXR \times \ARMNUM s+ \sum_{t=1}^{T}\TieDensity\cdot (g(t))^2 \nonumber \\ 
\leq & \sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  + \frac{128\Diam^2 d^2\sigma^2 \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t} \nonumber \\
\leq &  24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1) \nonumber \\
\leq &  12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). \nonumber
\end{align}

Thus, the cumulative expected regret is bounded by $O(\ARMNUM^2 d + \TieDensity d^2(\log(T))^2)$.
\end{proof}

\begin{corollary}
If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.
\end{corollary}

>>>>

@@

Let $\tau$ be any stopping time that is almost surely \dkcomment{What
  exactly do we mean by this here?} in phase $s$,
with respect to the filtration
$\mathcal{F}_{t} = \sigma (\Pull{1}, \ldots, \Pull{t},
                          \PayA{1}, \ldots, \PayA{t},
                          \ObsV{1}, \ldots, \ObsV{t})$.
Then, for all $s \geq \LatePhase$,
with probability (over the past history) at least 
$1 - 24 \ARMNUM d \exp\left(-\frac{1.8 s x^2}{16 \sigma^2} \right)$,
\dkcomment{We should clarify what the probability is over. It seems to
  be over the past history, but not the current agent.}
an agent of type $\AgV = \AgentV{\tau}$ 
will not pull a highly suboptimal arm, i.e., an arm $i$ with 
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
\end{corollary}

@@

Consider any agent type $\AgV = \AgentV{\tau}$ at the (random) time
$\tau$.
Let $i \neq \Best{\AgV}$ be any arm
with much smaller true reward than the best arm:
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i}) > 2\Diam d x$.
Because each coordinate of \ArmEV{\tau}{\Best{\AgV}} and of
\ArmEV{\tau}{i} is estimated accurately to within $x$, 
we get that 
$\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
\geq - \Diam d x$
and
$\AgV \cdot (\ArmEV{\tau}{i} - \ArmV{i}) \leq \Diam d x$.
Hence,

\begin{align}
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmEV{\tau}{i})
& =
\AgV \cdot (\ArmEV{\tau}{\Best{\AgV}} - \ArmV{\Best{\AgV}})
+ \AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{i})
+ \AgV \cdot (\ArmV{i} - \ArmEV{\tau}{i}) \nonumber\\
& > -\Diam d x + 2 \Diam d x - \Diam d x
\; = \; 0, \label{equ:choice}
\end{align}
which means that the agent with type \AgV will not pull arm $i$
under the high-probability event.
\end{proof}

@@

\dkcomment{The following paragraph is from Bangrui's version. It may
  move to an earlier section, go away, or become a part somewhere.}
As we can see later in our proof, we only need
$\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be
finite.
Intuitively, Assumption~\ref{A1} states that there are not many agents
who are indifferent between their best arm and the second best arm.

@@

We distinguish between agents incurring large regret
(which requires severe misestimates of arm locations;
such misestimated are exponentially unlikely to occur), 
and agents incurring small positive regret,
which requires these agents to be almost tied in their preference for
the best arm.
To be more precise, we will define (with hindsight) a time-dependent
cutoff $g(t)$, and consider a regret exceeding $g(t)$ large.

We first consider agents \AgV incurring positive regret less than $g(t)$.
The second-best arm \Second{\AgV} of \AgV must satisfy
$\AgV \cdot (\ArmV{\Best{\AgV}} - \ArmV{\Second{\AgV}}) \leq g(t)$.
By Lemma~\ref{lem:sdelta}, the total measure of such agents
is $\AlmostTied{g(t)} \leq \TieDensity \cdot g(t)$,
and each incurs regret at most $g(t)$.
Summing over all time steps, the total regret from such agents is at most
$\sum_{t = 1}^T \TieDensity \cdot g^2(t)$.

To bound the regret incurred in time steps with large regret,
let the random variable $t_s$ be the final time step in phase $s$,
for each $s$.
\dkcomment{Is $t_s$ better or $T_s$?}
Define the stopping times $\tau_{s}^{k}$ to be the \Kth{k}
time step in the \Kth{s} phase,
with $\tau_{s}^{k} = \infty$ when phase $s$ has fewer than $k$ steps,
i.e., $k > t_{s}-t_{s-1}$.
For $t = \tau_{s}^{k}$, by Corollary~\ref{cor:right-choice}
(applied with $x = \frac{g^2(\tau_s^k)}{4 \Diam^2 d^2}$),
the probability of incurring regret exceeding $g(t)$ is at most
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(\tau_{s}^{k})^2}{64 \Diam^2 d^2\sigma^2}\right)$.
Because each arm must have been pulled at least $s$ times by the time
the algorithm reaches phase $s$,
\dkcomment{Really only $s-1$; we have to be careful with those $\pm 1$.}
we can bound $\tau_{s}^{k} \geq s$.
\dkcomment{We could bound it by $\ARMNUM s$, if that helps get
  slightly better bounds.}
Because the regret never exceeds \MAXR,
the expected (large) regret for the \Kth{k} time step of phase $s$
is bounded above by
$24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g(s)^2}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR$.
Summing over all time steps $t$, we get that the total regret from
large-regret steps is at most

\begin{align*}
\lefteqn{\sum_{s = \LatePhase}^T \sum_{t=t_s}^{t_{s+1}-1}
  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR}
\\ & =
\sum_{s = \LatePhase}^T 
  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
  \cdot \Expect{\mbox{Length of phase } s}
\\ & \leq
\sum_{s = \LatePhase}^T 
  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
  \cdot \ARMNUM s,
\end{align*}
where the inequality was an application of Lemma~\ref{lem:phase-length}.
Adding all four terms, and starting the sum at 1 instead of \LatePhase,
the cumulative regret up to time $T$ is at most

\begin{multline*}
O(\ARMNUM \MAXR \LatePhase^2) + 
O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) +
\\
+ \sum_{s = 1}^T 
  24 \ARMNUM d \cdot \exp\left(-\frac{1.8 s g^2(s)}{64 \Diam^2 d^2\sigma^2}\right) \cdot \MAXR
  \cdot \ARMNUM s,
+ \sum_{t=1}^{T}\TieDensity \cdot g^2(t).
\end{multline*}

The first line is independent of $T$, and we now choose
$g^2(t) = \frac{2\log(T) \cdot 64 \Diam^2 d^2 \sigma^2}{1.8 t}$
with the goal of minimizing the second line.
With this choice, the second line becomes

\begin{align*}
\lefteqn{\sum_{s=1}^{T} 24\ARMNUM^2 d s \MAXR \exp\left(-2\log(T)\right)  +
          \frac{128\Diam^2 d^2\sigma^2
          \TieDensity\log(T)}{1.8}\sum_{t=1}^{T}\frac{1}{t}}
\\ & \leq
24\ARMNUM^2 d R\frac{T(T-1)}{2T^2}  + 71.12 \Diam^2 d^2\sigma^2
          \TieDensity\log(T)(\log(T)+1)
  \\ & \leq
12 \ARMNUM^2 d R  + 71.12 \Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1). 
\end{align*}

Adding all terms, and substituting the definition of
$\LatePhase = O(\frac{\sigma^4}{x^4})$
now gives an upper bound of

\begin{multline*}
O(\ARMNUM \MAXR \LatePhase^2) + 
O \left( \frac{\MAXR \ARMNUM \TieDensity^4 \Diam^4 d^4 \sigma^4}{\MinProb^4}
  + \frac{\MAXR \ARMNUM^2 d}{1 - \exp \left(
    \frac{-1.8 s \cdot \MinProb^2}{256 \TieDensity^2 \Diam^2 d^2 \sigma^2}
  \right)} \right) +
O(\Diam^2 d^2\sigma^2 \TieDensity\log(T)(\log(T)+1)) 
\end{multline*}

on the cumulative expected regret.
\dkcomment{I see a problem here: What's the value of $x$ in the
  definition of \LatePhase? Presumably, we need to make $x$ small
  enough that any $x$ we use in any application of Lemma 7 (or
  Corollary 10) works. But notice that we use $x =
  \Theta(g^2(\tau_s^k))$,
  and in particular for the last step, I don't see how we can make
  $\tau_s^k$ much smaller than $T$.
  But then, we get that $x = O(\frac{\log T}{T})$, which would give
  linear regret. How to handle this?}
\end{proof}

\dkcomment{Edited up to here.}

\begin{corollary} \label{cor:constant-regret}
If $\exists \delta>0$ such that $F_{i,j}(\delta)=0$ for all $i,j$, then the cumulative expected regret is bounded by $O(\ARMNUM^2)$.
\end{corollary}

### 2018-02-06 lower_bound.tex
almost finished regret proof

\newcommand{\dd}{\mathrm{d}}
\newcommand{\quarter}{\ensuremath{\frac{1}{4}}\xspace}

@@

We saw in Corollary~\dkcomment{assign a label and insert here} that
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that that regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.

We consider an instance with two arms,
whose attribute vectors are $(0,0)$ and $(0,1)$, respectively.
Agents types are distributed uniformly on the two-dimensional unit circle%
\footnote{While our model technically assumed that all agent coordinates are
non-negative, we could simply shift the unit circle.
The present choice is solely for ease of notation.}  
$\Set{\AgV}{|| \AgV ||_2 \leq 1}$.
Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
\dkcomment{modify macro to do this correctly}
the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
i.e., the top half of the unit circle prefers the arm $(0,1)$,
and the bottom half prefers the arm $(0,0)$.

@@

Because a pull of arm $(0,1)$ is observed in each time step,
after $t$ rounds, the estimate \ArmEV{t+1}{(0,1)} is of the form
$(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
where $\Noise[t]{1} \sim \Normal{0}{1/t}$
and $\Noise[t]{2} \sim \Normal{0}{1/t})$.
We lower-bound the regret in step $t$ by focusing on the event that
both normal noise coordinates are non-negative,
which by symmetry has probability \quarter:

@@

For the moment, focus on some time step $t$,
and write $\NoiseV = \NoiseV[t]$.
Then, there are two types of agents who pull the wrong arm and incur
regret:
\begin{enumerate}
\item If $\Ag{2} > 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) < 0$
then \Ag should pull $(0,1)$,
but will wrongly pull $(0,0)$ and incur regret \Ag{2}.
The region
$\Ag{2} > 0$ and $\Ag{1} < \frac{-(1+\Noise{2})}{\Noise{1}} \cdot \Ag{2}$
defines a wedge.
For any particular value of \Ag{2},
the length of the interval of corresponding \Ag{1} is
\begin{align*}
  \sqrt{1-\Ag{2}^2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
  & \geq 1 - \Ag{2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
  \; = \; 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2}.
\end{align*}

@@

Hence, the expected regret for given \Noise{1}, \Noise{2} is at least
\begin{align*}
  2 \int_0^{\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}}
  \left( 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2} \right)
  \cdot \Ag{2} \cdot \frac{1}{\pi} \dd \Ag{2}
& =
\frac{1}{\pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
- \frac{2}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2
\\ & =
\frac{1}{3 \pi} \cdot \left(\frac{1+\Noise{1}+\Noise{2}}{\Noise{1}}\right)^2.
\end{align*}

>>>>

@@

We saw in Corollary~\ref{cor:constant-regret} that
when agent preferences for their best arm are sufficiently clear,
in the sense that $\TieDensity = 0$, the regret of
Algorithm~\ref{alg:basic-incentivizing} is bounded by a constant.
One may conjecture that this should hold more generally,
in that that regret of the (fewer and fewer) agents on the boundary
between close arms should go to 0, while their fraction also goes to 0.
In this section, we establish a lower bound,
showing that even in very simple settings, a (logarithmic) dependence
on $T$ is typicaly unavoidable for \emph{any} incentivization strategy.

We consider an instance with two arms,
whose attribute vectors are $(0,0)$ and $(0,1)$, respectively.
Agents types are distributed uniformly on the two-dimensional unit circle%
\footnote{While our model technically assumed that all agent coordinates are
non-negative, we could simply shift the unit circle.
The present choice is solely for ease of notation.}  
$\Set{\AgV}{|| \AgV ||_2 \leq 1}$.
Because $\AgV \cdot (0,0) = 0$ and $\AgV \cdot (0,1) = \Ag{2}$,
the best choice for agent \AgV is arm $(0,1)$ iff $\Ag{2} > 0$,
i.e., the top half of the unit circle prefers the arm $(0,1)$,
and the bottom half prefers the arm $(0,0)$.

@@

Because a pull of arm $(0,1)$ is observed in each time step,
after $t$ rounds, the estimate \ArmEV{t}{(0,1)} is of the form
$(0,1) + (\Noise[t]{1}, \Noise[t]{2})$,
where $\Noise[t]{1} \sim \Normal{0}{\sqrt{1/t}}$
and $\Noise[t]{2} \sim \Normal{0}{\sqrt{1/t}})$.
\dkcomment{I think we define this to be the estimates at the beginning
  of round $t$, so we may be off by 1 here and in other places.}
We lower-bound the regret in step $t$ by focusing on the event that
both normal noise coordinates are non-negative,
which by symmetry has probability \quarter:

@@

For the moment, focus on some time step $t$,
and write $\NoiseV = \NoiseV[t]$.
Then, there are two types of agents who pull the wrong arm and incur
regret:
\begin{enumerate}
\item If $\Ag{2} > 0$ and $\Ag{1} \Noise{1} + \Ag{2} (1+\Noise{2}) < 0$
then \AgV should pull $(0,1)$,
but will wrongly pull $(0,0)$ and incur regret \Ag{2}.
The region
$\Ag{2} > 0$ and $\Ag{1} < \frac{-(1+\Noise{2})}{\Noise{1}} \cdot \Ag{2}$
defines a wedge.
For any particular value of \Ag{2},
the length of the interval of corresponding \Ag{1} is
\begin{align*}
  \sqrt{1-\Ag{2}^2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
  & \geq 1 - \Ag{2} - \frac{1+\Noise{2}}{\Noise{1}} \cdot \Ag{2}
  \; = \; 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2}.
\end{align*}

@@

Hence, the expected regret for given \Noise{1}, \Noise{2} is at least
\begin{align*}
  2 \int_0^{\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}}
  \left( 1 - \frac{1+\Noise{1}+\Noise{2}}{\Noise{1}} \cdot \Ag{2} \right)
  \cdot \Ag{2} \cdot \frac{1}{\pi} \dd \Ag{2}
& =
\frac{1}{\pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
- \frac{2}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2
\\ & =
\frac{1}{3 \pi} \cdot \left(\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}}\right)^2.
\end{align*}
